Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing_jsa.tex
fixes #172

To illustrate the concept, we show a simple likelihood function in
Table~\ref{probabilitybrazilian}.  The null would be that this reified
entity has zero strength.  We fail to reject this null (differential
support = 0.035; $p=0.79$) and conclude that there is no evidence to
suggest that Brazilians' performance is better on their preferred wave
types than one would expect by chance.  We may go further using the
method of support: not only is the maximum likelihood estimate for
Brazilian wavetype very small (about 0.002), but in addition we may
reject the the proposal that the strength of this entity exceeds about
0.025 (Figure~\ref{brazilian_wavetype_support}).

@@

\begin{figure}[h]
  \includegraphics[width=4in]{plotwidep.pdf}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis}
\end{figure}

>>>>

To illustrate the concept, we show a simple likelihood function in
Table~\ref{probabilitybrazilian}.  The null would be that this reified
entity has zero strength.  We fail to reject this null (differential
support = 0.035; $p=0.79$) and conclude that there is no evidence to
suggest that Brazilians' performance is better on their preferred wave
types than one would expect by chance.  We may go further using the
method of support: not only is the maximum likelihood estimate for
Brazilian wavetype very small (about 0.002), but in addition we may
reject the the proposal that the strength of this entity exceeds about
0.015 (Figure~\ref{brazilian_wavetype_support}): at this value of the
strength or greater, we may gain two or more units of support by
moving to the evaluate~\citep{edwards1992}.

@@

\begin{figure}[h]
  \includegraphics[width=4in]{plotwidep.pdf}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis.  At a strength of
  0.015 we see the support is $-2$ and we could thus be reasonably
  confident that the strength does not exceed this value.}
\end{figure}
